Lista de Exercícios

### 2017-03-10 exercises.Rmd
Modify preamble, the margins are defined for each document now

---
title: 'Lista de Exercícios'
academic: Eduardo Elias Ribeiro Junior
email: 'edujrrib@gmail.com'
chair: LCE5859 - Métodos Estatísticos Multivariados
institute: 'Escola Superior de Agricultura Luiz de Queiroz - USP'
date: '\today'
logo: "configs/logo-esalq.png"
bibliography: lce5859-mem.bib
csl: configs/abntcite.csl
output:
  pdf_document:
    template: configs/template.tex
    keep_tex: false
---

>>>>

---
title: 'Lista de Exercícios'
academic: Eduardo Elias Ribeiro Junior
email: 'edujrrib@gmail.com'
chair: LCE5859 - Métodos Estatísticos Multivariados
institute: 'Escola Superior de Agricultura Luiz de Queiroz - USP'
date: '\today'
logo: "configs/logo-esalq.png"
bibliography: lce5859-mem.bib
csl: configs/abntcite.csl
header-includes:
  - \usepackage[hmargin={1.7cm, 1.7cm}, vmargin={1.7cm, 1.7cm}]{geometry}
output:
  pdf_document:
    template: configs/template.tex
    keep_tex: false
---
